Detection of Treatment-Subgroup Interactions in Clustered Datasets with Generalized Linear Mixed-effects Model Trees (GLMM trees)

### 2015-08-28 pkg/glmertree/paper/treatment_interactions.Rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@764 255f4249-2263-4417-b1ea-8498779e27a7

Where $z_{i}$ is a unit vector of length $M$, of which the $m$th element takes a value of 1, and all other elements take a value of 0, with $m$ ($m=1,...,M$) denotes the cluster of which observation $i$ is part. $b$ is random vector of length $M$, each element being the random intercept for $m$. Within the GLMM, it is assumed that $b$ is normally distributed, with mean zero and variance $\sigma^{2}_{b}$. The parameters of the GLMM can be estimated with, for example, maximum likelihood (ML) and restricted ML (REML), as described in \citeA{BrykyRaud92}, for example.

>>>>

Where $z_{i}$ is a unit vector of length $M$, of which the $m$th element takes a value of 1, and all other elements take a value of 0; $m$ ($m=1,...,M$) denotes the cluster of which observation $i$ is part. $b$ is random vector of length $M$, each element being the random intercept for $m$. Within the GLMM, it is assumed that $b$ is normally distributed, with mean zero and variance $\sigma^{2}_{b}$. The parameters of the GLMM can be estimated with, for example, maximum likelihood (ML) and restricted ML (REML), as described in \citeA{BrykyRaud92}, for example.
